SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 back.tex
Fixed minor grammatical error

\noindent \textbf{Lookahead Prefetching:} On each trigger, SPP goes
down the program speculation path using its own prefetch suggestion.
Using current prefetch as a starting point, it re-accesses the Pattern
Table to generate further prefetches.  As illustrated in
Figure~\ref{fig:spp_structure}, it repeats the cycle of accessing
Pattern Table and updating the signature based on highest confidence
prefetch from the last iteration.  The iteration counter on which SPP
manages to predict prefetch entries in the lookahead manner is
characterized as its `depth'. While doing so, SPP also keeps
compounding the confidence in each depth. Thus as depth increases,
overall confidence keeps decreasing.

@@

As was noted in Figure~\ref{Fig:Motivation}, an aggressive lookahead
prefetching, if done without any accuracy check, can harm the
performance of the system. As the figure shows, aggressive lookahead
and its accompanied loss of accuracy degrades performance by almost
9\%.  This is despite a growing number of useful prefetches generated
by the prefetcher.  Thus, we need a mechanism that is orthogonal to
the underlying prefetching scheme and can be used to prune out the
useful prefetches from the useless ones.

>>>>

\noindent \textbf{Lookahead Prefetching:} On each trigger, SPP goes
down the program speculation path using its own prefetch suggestion.
Using the current prefetch as a starting point, it re-accesses the Pattern
Table to generate further prefetches.  As illustrated in
Figure~\ref{fig:spp_structure}, it repeats the cycle of accessing
Pattern Table and updating the signature based on highest confidence
prefetch from the last iteration.  The iteration counter on which SPP
manages to predict prefetch entries in the lookahead manner is
characterized as its `depth'. While doing so, SPP also keeps
compounding the confidence in each depth. Thus as depth increases,
overall confidence keeps decreasing.

@@

As was noted in Figure~\ref{Fig:Motivation}, aggressive lookahead
prefetching, if done without any accuracy check, can harm the
performance of the system. As the figure shows, aggressive lookahead
and its accompanied loss of accuracy degrades performance by almost
9\%.  This is despite a growing number of useful prefetches generated
by the prefetcher.  Thus, we need a mechanism that is orthogonal to
the underlying prefetching scheme and can be used to prune out the
useful prefetches from the useless ones.
